Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
e.g.,

The classical approach to control synthesis has often disregarded quantization, 
thus resulting in general to unsound digital controllers. 
Modern techniques focus on different elements of discretization effects, including delayed
response~\cite{Duggirala2015}, and Finite Word Length (FWL) semantics, 
with the goal either to verify (e.g.~\cite{daes20161}) or to optimize
(e.g.~\cite{oudjida2014design}) given implementations.

>>>>

The classical approach to control synthesis has often disregarded quantization, 
thus resulting in general to unsound digital controllers. 
Modern techniques focus on different elements of discretization effects, including delayed
response~\cite{Duggirala2015}, and Finite Word Length (FWL) semantics, 
with the goal either to verify (e.g.,~ \cite{daes20161}) or to optimize
(e.g.,~ \cite{oudjida2014design}) given implementations.
